### 2021-06-27 submission/manuscript.Rmd
Incorporate edits from coauthors

## Abstract
Antibiotics are a major risk factor for *Clostridioides difficile* infections (CDIs) because of their impact on the microbiota. However, non-antibiotic medications such as the ubiquitous osmotic laxative polyethylene glycol (PEG) 3350 also alter the microbiota. But whether PEG impacts CDI susceptibility and clearance is unclear. To examine how PEG impacts susceptibility, we treated C57Bl/6 mice with 5-day and 1-day doses of 15% PEG in the drinking water and then challenged the mice with *C. difficile* 630. We used clindamycin-treated mice as a control because they consistently clear *C. difficile* within 10 days post-challenge. PEG treatment alone was sufficient to render mice susceptible and 5-day PEG-treated mice remained colonized for up to 30 days post-challenge. In contrast, 1-day PEG treated mice were transiently colonized, clearing *C. difficile* within 7 days post-challenge. To examine how PEG treatment impacts clearance, we administered a 1-day PEG treatment to clindamycin-treated, *C. difficile*-challenged mice. Administering PEG to mice after *C. difficile* challenge prolonged colonization up to 30 days post-challenge. When we trained a random forest model with community data from 5 days post-challenge, we were able to predict which mice would exhibit prolonged colonization (AUROC = 0.90). Examining the dynamics of these bacterial populations during the post-challenge period revealed patterns in the relative abundances of *Bacteroides*, *Enterobacteriaceae*, *Porphyromonadaceae*, *Lachnospiraceae*, and *Akkermansia* that were associated with prolonged *C. difficile* colonization in PEG-treated mice. Thus, the osmotic laxative, PEG, rendered mice susceptible to *C. difficile* colonization and hindered clearance.

## Importance
Diarrheal samples from patients taking laxatives are typically rejected for *Clostridiodes difficile* testing. However, there are similarities between the bacterial communities from people with diarrhea or *C. difficile* infections (CDI) including lower diversity compared to communities from healthy patients. This observation led us to hypothesize that diarrhea may be an indicator of *C. difficile* susceptibility. We explored how osmotic laxatives disrupt the microbiota's colonization resistance to *C. difficile* by administering a laxative to mice either before or after *C. difficile* challenge. Our findings suggest that osmotic laxatives disrupt colonization resistance to *C. difficile*, and prevent clearance among mice already colonized with *C. difficile*. Considering that most hospitals recommend not performing *C. difficile* testing on patients taking laxatives and laxatives are used when administering fecal microbiota transplants via colonoscopy to patients with recurrent CDIs, further studies are needed to evaluate if laxatives impact microbiota colonization resistance in humans.

@@

Many of the non-antibiotic medications associated with CDIs are known to modulate gastrointestinal motility leading to either increased or decreased colonic transit time, which in turn also strongly impacts microbiota composition and function [@Vandeputte2015; @VujkovicCvijin2020]. Stool consistency often serves as an approximation of intestinal motility [@Vandeputte2015]. Our group has shown that when *C. difficile* negative samples from patients were separated into two groups based on stool consistency, there were similar microbiota features between samples from CDI patients and *C. difficile* negative patients with diarrhea compared to non-diarrheal samples that were *C. difficile* negative [@Schubert2014]. The similar community features between CDI patients and patients with diarrhea included low alpha diversity and there were also only 6 bacterial taxa had higher relative abundances in communities from CDI patients. These results led to the hypothesis that bacterial communities from patients experiencing diarrhea are susceptible to developing CDIs, regardless of how they developed diarrhea.

@@

Beyond susceptibility, PEG is also relevant in the context of treating recurrent CDIs via fecal microbiota transplant (FMT) where a healthy microbiota is administered to the patient to restore colonization resistance. For FMTs that are delivered via colonoscopy, patients typically undergo bowel preparation by taking an osmotic laxative prior to the procedure. Many of the FMT studies to date rationalize the use of laxatives prior to the FMT [@vanNood2013; @Razik2017; @Postigo2012] based on a 1996 case study with 2 pediatric patients where the authors suggested in the discussion that the laxative may help flush *C. difficile* spores and toxins from the intestine [@Liacouras1996].

@@

```
**5-day laxative treatment differentially disrupted the fecal microbiota compared to clindamycin treatment.** Since osmotic laxatives and clindamycin have previously been shown to disrupt the murine microbiota [@Kashyap2013; @Ferreyra2014; @Tropini2018; @VanInsberghe2020], we hypothesized the different *C. difficile* colonization dynamics between mice treated with the osmotic laxative or clindamycin were due to the two drugs having differential effects on the microbiota. We profiled the stool microbiota over time by sequencing the V4 region of the 16S rRNA gene to compare changes across treatment groups. We found time (R^2^ = `r r2_day`) and treatment group (R^2^ = `r r2_group`) explained half of the observed variation between fecal communities with most of the remaining variation explained by interactions between treatment group and other experimental variables including time, cage, and sequencing preparation plate (PERMANOVA combined R^2^ = `r f_d_top_R2_sum`, *P* `r format.pval(f_d_top_p, eps = 0.001)`, Fig. 2A, Data Set S1, sheet 1). None of the treatment groups recovered to their baseline community structure either 10 or 30 days post-challenge suggesting other community features besides recovery to baseline were responsible for the prolonged *C. difficile* colonization in PEG-treated mice (Fig. 2B).

@@

Because *C. difficile* was not immediately detectable in the stools of the PEG-treated mice that were allowed to recover for 10 days prior to  challenge, we decided to examine if there were genera that changed during the post-challenge period. We compared the communities from when *C. difficile* shifted from undetectable at 1 day post-challenge to detectable in the stool samples with the density stabilizing around 8 days post-challenge (Fig. S1A). We found no genera with relative abundances that were significantly different over the two time points (Data Set S1, sheet 5). However, there was also wide variation between individual mice regarding when *C. difficile* became detectable (Fig. S1A) as well as the relative abundances of bacterial genera in the communities (Fig. S1B). For example, two mice had a high relative abundance of *Enterobacteriaceae* throughout the post-challenge period. One mouse died on the sixth day post-challenge and in the other *C. difficile* was present at a high density from the 4th day post-challenge onward (Fig. S1B). While we did not identify a clear signal to explain the delayed appearance of *C. difficile* in the 5-day PEG mice that were allowed to recover for 10 days prior to challenge, the delay was striking and could reflect changes in microbial activity or metabolites that were not examined in this study.

@@

Because there were differences in the mucosal microbiota including detectable *C. difficile* sequences in tissues from PEG-treated mice relative to mice treated with clindamycin, we next examined the severity of *C. difficile* challenge by evaluating cecum and colon histopathology [@Reeves2011]. However, we found there was no difference in cecum and colon scores between clindamycin and PEG-treated mice that were challenged with *C. difficile* at 4 days post-challenge (Fig. 3D), the time point typically examined in *C. difficile* 630 challenged mice [@Dieterle2020]. We also looked at 6 days post-challenge because that was when there was a large difference in *C. difficile* density between PEG- and clindamycin-treated mice (Fig. 1C). Although there was a slight difference in the histopathology score of the colon between PEG and clindamycin-treated mice, there was not a signifant difference in the cecum and the overall score was relatively low (1.5 to 2.5 out of 12, Fig. 3E). Therefore, although PEG treatment had a disruptive effect on the mucosal microbiota, the impact of *C. difficile* challenge on the cecum and colon was similar between PEG and clindamycin treated mice.

@@

## Discussion
While the disruptive effect of antibiotics on *C. difficile* colonization resistance is well established, the extent to which other drugs such as laxatives disrupt colonization resistance was unclear. By following mice treated with an osmotic laxative over time, we found that a 5-day PEG treatment before challenge resulted in prolonged *C. difficile* colonization, while a 1-day PEG treatment resulted in transient colonization without the use of antibiotics. The differences in *C. difficile* colonization dynamics between the 5- and 1-day PEG treated mice were associated with differences in how much the treatments disrupted the microbiota. Additionally, the intestinal communities of 5-day PEG treated mice did not regain colonization resistance after a 10-day recovery period. In contrast to the other 5-day PEG treatment groups, *C. difficile* was not immediately detectable in the stools of most of the mice in the 10-day recovery group. We also examined the impact of PEG treatment after *C. difficile* challenge. In opposition to the hypothesis suggested by the literature, we found that PEG treatment prolonged colonization relative to mice that only recieved clindamycin treatment. We identified patterns in the relative abundances of *Bacteroides*, *Enterobacteriaceae*, *Akkermansia*, *Porphyromonadaceae*, and *Lachnospiraceae* that were associated with prolonged *C. difficile* colonization (Fig. 8). Overall, our results demonstrated that osmotic laxative treatment alone rendered mice susceptible to *C. difficile* colonization and the duration of colonization depended on the length of PEG treatment and whether treatment was administered before or after challenge.

In addition to altering composition, laxative treatment may alter microbiota-produced metabolites. A previous study demonstrated that a 5-day treatment of 10% PEG depleted acetate and butyrate and increased succinate compared to untreated mice [@Ferreyra2014]. While we did not perform metabolomic analysis, we did see bacteria known to produce benefical metabolites were depleted in mice that cleared *C. difficile* compared to mice with prolonged colonization. For example, *Oscillibacter valericigenes* can produce the SCFA valerate [@Iino2007], and separate studies demonstrated valerate is depleted after clindamycin treatment and inhibited *C. difficile* growth *in vitro* and in C57BL/6 mice [@Jump2014; @McDonald2018]. Similarly, *Acetatifactor* can produce acetate and butyrate [@Pfeiffer2012], SCFAs that are decreased in mice with prolonged *C. difficile* infection after antibiotic treatment [@Lawley2012]. Thus protective bacteria and their metabolites could be depleted by osmotive laxative treatment depending on the timing and duration of treatment.

One possible explanation for the prolonged *C. difficile* colonization in 5-day PEG treated mice, might be due to the bacteria's persistence in the mucosal compartment. In fact, it has been hypothesized that *C. difficile* biofilms may serve as reservoirs for recurrent infections [@Frost2021] and *C. difficile* biofilms in the mucus layer were recently identified in patients as aggregates with *Fusobacterium nucleatum* [@Engevik2021]. There was an interesting pattern of increased *Enterobacteriaceae*, *Bacteroides*, and *C. difficile* in both the stool and mucosal communities of PEG-treated mice suggesting a potential synergy. *Bacteroides* has the potential to degrade mucus and the osmotic laxative may have allowed *Bacteroides* to colonize the mucosal niche by degrading mucin glycans with glycosyl hydrolases that are absent in *C. difficile* [@Engevik2020]. *Bacteroides* persistence in the mucosal tissue might also have helped *Enterobacteriaceae* to colonize the region, as a synergy between mucus-degrading *B. fragilis* and *E. coli* has previously been described [@Dejea2018]. A separate study demonstrated *C. difficile* was present in the outer mucus layer and associated with *Enterobacteriaceae* and *Bacteroidaceae* using fluorescent in situ hybridization (FISH) staining [@Semenyuk2015]. However, protective roles for *Bacteroides* have also been demonstrated. For example, *B. fragilis* prevented CDI morbidity in a mouse model and inhibited *C. difficile* adherence *in vitro* [@Deng2018]. In coculture experiments *B. longum* decreased *C. difficile* biofilm formation while *B. thetaiotamicron* enhanced biofilm formation [@Normington2021] and *B. dorei* reduced *C. difficile* growth in a 9-species community *in vitro* [@Hassall2021]. Therefore, whether *Bacteroides* is detrimental or beneficial in the context of *C. difficile* infection or colonization is still unclear, but the niche and interactions with other bacteria may contribute.

*Akkermansia* is also a mucin degrader with potentially beneficial or detrimental roles depending on context in other diseases [@Cirstea2018; @BorgesCanha2015]. In our study the relative abundance of *Akkermansia* shifted over time between groups of mice that either cleared *C. difficile* or had prolonged colonization. In the stool it was initially increased in mice that cleared *C. difficile*, but shifted after 5-days post-challenge so that it was increased in mice that had prolonged colonization. In the context of CDIs, some studies suggest a protective role [@Pereira2020; @Rodriguez2016], while others suggest a detrimental role because *Akkermansia* was positively correlated with *C. difficile* [@Sangster2016; @Vakili2020a; @Vakili2020b; @Li2019]. Because the relative abundance of *Akkermansia* was dynamic in our study, it is unclear whether *Akkermansia* helps with clearance of *C. difficile* or allows it to persist. A better understanding how *C. difficile* interacts with the mucosal microbiota may lead to insights into CDIs, asymptomatic *C. difficile* carriage, and colonizatiion resistance.

>>>>

## Abstract
Antibiotics are a major risk factor for *Clostridioides difficile* infections (CDIs) because of their impact on the microbiota. However, non-antibiotic medications such as the ubiquitous osmotic laxative polyethylene glycol (PEG) 3350 also alter the microbiota. Clinicians also hypothesize that PEG helps clear *C. difficile*. But whether PEG impacts CDI susceptibility and clearance is unclear. To examine how PEG impacts susceptibility, we treated C57Bl/6 mice with 5-day and 1-day doses of 15% PEG in the drinking water and then challenged the mice with *C. difficile* 630. We used clindamycin-treated mice as a control because they consistently clear *C. difficile* within 10 days post-challenge. PEG treatment alone was sufficient to render mice susceptible and 5-day PEG-treated mice remained colonized for up to 30 days post-challenge. In contrast, 1-day PEG treated mice were transiently colonized, clearing *C. difficile* within 7 days post-challenge. To examine how PEG treatment impacts clearance, we administered a 1-day PEG treatment to clindamycin-treated, *C. difficile*-challenged mice. Administering PEG to mice after *C. difficile* challenge prolonged colonization up to 30 days post-challenge. When we trained a random forest model with community data from 5 days post-challenge, we were able to predict which mice would exhibit prolonged colonization (AUROC = 0.90). Examining the dynamics of these bacterial populations during the post-challenge period revealed patterns in the relative abundances of *Bacteroides*, *Enterobacteriaceae*, *Porphyromonadaceae*, *Lachnospiraceae*, and *Akkermansia* that were associated with prolonged *C. difficile* colonization in PEG-treated mice. Thus, the osmotic laxative, PEG, rendered mice susceptible to *C. difficile* colonization and hindered clearance.

## Importance
Diarrheal samples from patients taking laxatives are typically rejected for *Clostridiodes difficile* testing. However, there are similarities between the bacterial communities from people with diarrhea or *C. difficile* infections (CDI) including lower diversity compared to communities from healthy patients. This observation led us to hypothesize that diarrhea may be an indicator of *C. difficile* susceptibility. We explored how osmotic laxatives disrupt the microbiota's colonization resistance to *C. difficile* by administering a laxative to mice either before or after *C. difficile* challenge. Our findings suggest that osmotic laxatives disrupt colonization resistance to *C. difficile*, and prevent clearance among mice already colonized with *C. difficile*. Considering that most hospitals recommend not performing *C. difficile* testing on patients taking laxatives and laxatives are prescribed prior to administering fecal microbiota transplants via colonoscopy to patients with recurrent CDIs, further studies are needed to evaluate if laxatives impact microbiota colonization resistance in humans.

@@

Many of the non-antibiotic medications associated with CDIs are known to modulate gastrointestinal motility leading to either increased or decreased colonic transit time, which in turn also strongly impacts microbiota composition and function [@Vandeputte2015; @VujkovicCvijin2020]. Stool consistency often serves as an approximation of intestinal motility [@Vandeputte2015]. Our group has shown that when *C. difficile* negative samples from patients were separated into two groups based on stool consistency, there were similar microbiota features between samples from CDI patients and *C. difficile* negative patients with diarrhea compared to non-diarrheal samples that were *C. difficile* negative [@Schubert2014]. The similar community features between CDI patients and patients with diarrhea included low alpha diversity and only 6 bacterial taxa with higher relative abundances in communities from CDI patients. These results led to the hypothesis that bacterial communities from patients experiencing diarrhea are susceptible to developing CDIs, regardless of how they developed diarrhea.

@@

Beyond susceptibility, PEG is also relevant in the context of treating recurrent CDIs via fecal microbiota transplant (FMT), where a healthy microbiota is administered to the patient to restore colonization resistance. For FMTs that are delivered via colonoscopy, patients typically undergo bowel preparation by taking an osmotic laxative prior to the procedure. Many of the FMT studies to date rationalize the use of laxatives prior to the FMT [@vanNood2013; @Razik2017; @Postigo2012] based on a 1996 case study with 2 pediatric patients where the authors suggested in the discussion that the laxative may help flush *C. difficile* spores and toxins from the intestine [@Liacouras1996].

@@

```
**5-day laxative treatment differentially disrupted the fecal microbiota compared to clindamycin treatment.** Since osmotic laxatives and clindamycin have previously been shown to disrupt the murine microbiota [@Kashyap2013; @Ferreyra2014; @Tropini2018; @VanInsberghe2020], we hypothesized the different *C. difficile* colonization dynamics between mice treated with the osmotic laxative or clindamycin were due to the two drugs having differential effects on the microbiota. We profiled the stool microbiota over time by sequencing the V4 region of the 16S rRNA gene to compare changes across treatment groups. We found time (R^2^ = `r r2_day`) and treatment group (R^2^ = `r r2_group`) explained half of the observed variation between fecal communities with most of the remaining variation explained by interactions between treatment group and other experimental variables including time, cage, and sequencing preparation plate (PERMANOVA combined R^2^ = `r f_d_top_R2_sum`, *P* `r format.pval(f_d_top_p, eps = 0.001)`, Fig. 2A, Data Set S1, sheet 1). None of the treatment groups recovered to their baseline community structure either 10 or 30 days post-challenge, suggesting other community features besides recovery to baseline were responsible for the prolonged *C. difficile* colonization in PEG-treated mice (Fig. 2B).

@@

Because *C. difficile* was not immediately detectable in the stools of the PEG-treated mice that were allowed to recover for 10 days prior to  challenge, we decided to examine if there were genera that changed during the post-challenge period. We compared the communities from when *C. difficile* shifted from undetectable at 1 day post-challenge to detectable in the stool samples with the density stabilizing around 8 days post-challenge (Fig. S1A). We found no genera with relative abundances that were significantly different over the two time points (Data Set S1, sheet 5). However, there was also wide variation between individual mice regarding when *C. difficile* became detectable (Fig. S1A) as well as the relative abundances of bacterial genera in the communities (Fig. S1B). For example, two mice had a high relative abundance of *Enterobacteriaceae* throughout the post-challenge period. One mouse died on the sixth day post-challenge and in the other, *C. difficile* was present at a high density from the 4th day post-challenge onward (Fig. S1B). While we did not identify a clear signal to explain the delayed appearance of *C. difficile* in the 5-day PEG mice that were allowed to recover for 10 days prior to challenge, the delay was striking and could reflect changes in microbial activity or metabolites that were not examined in this study.

@@

Because there were differences in the mucosal microbiota, including detectable *C. difficile* sequences in tissues from PEG-treated mice relative to mice treated with clindamycin, we next examined the severity of *C. difficile* challenge by evaluating cecum and colon histopathology [@Reeves2011]. However, we found there was no difference in cecum and colon scores between clindamycin and PEG-treated mice that were challenged with *C. difficile* at 4 days post-challenge (Fig. 3D), the time point typically examined in *C. difficile* 630 challenged mice [@Dieterle2020]. We also looked at 6 days post-challenge because that was when there was a large difference in *C. difficile* density between PEG- and clindamycin-treated mice (Fig. 1C). Although there was a slight difference in the histopathology score of the colon between PEG and clindamycin-treated mice, there was not a signifant difference in the cecum and the overall score was relatively low (1.5 to 2.5 out of 12, Fig. 3E). Therefore, although PEG treatment had a disruptive effect on the mucosal microbiota, the impact of *C. difficile* challenge on the cecum and colon was similar between PEG and clindamycin treated mice.

@@

## Discussion
While the disruptive effect of antibiotics on *C. difficile* colonization resistance is well established, the extent to which other drugs such as laxatives disrupt colonization resistance was unclear. By following mice treated with an osmotic laxative over time, we found that a 5-day PEG treatment before challenge resulted in prolonged *C. difficile* colonization, while a 1-day PEG treatment resulted in transient colonization without the use of antibiotics. The differences in *C. difficile* colonization dynamics between the 5- and 1-day PEG treated mice were associated with differences in the degree to which treatments disrupted the microbiota. Additionally, the intestinal communities of 5-day PEG treated mice did not regain colonization resistance after a 10-day recovery period. In contrast to the other 5-day PEG treatment groups, *C. difficile* was not immediately detectable in the stools of most of the mice in the 10-day recovery group. We also examined the impact of PEG treatment after *C. difficile* challenge. In opposition to the hypothesis suggested by the literature, we found that PEG treatment prolonged colonization relative to mice that only recieved clindamycin treatment. We identified patterns in the relative abundances of *Bacteroides*, *Enterobacteriaceae*, *Akkermansia*, *Porphyromonadaceae*, and *Lachnospiraceae* that were associated with prolonged *C. difficile* colonization (Fig. 8). Overall, our results demonstrated that osmotic laxative treatment alone rendered mice susceptible to *C. difficile* colonization and the duration of colonization depended on the length of PEG treatment and whether treatment was administered before or after challenge.

In addition to altering composition, laxative treatment may alter microbiota-produced metabolites. A previous study demonstrated that a 5-day treatment of 10% PEG depleted acetate and butyrate and increased succinate compared to untreated mice [@Ferreyra2014]. While we did not perform metabolomic analysis, we did see bacteria known to produce beneficial metabolites were depleted in mice that cleared *C. difficile* compared to mice with prolonged colonization. For example, *Oscillibacter valericigenes* can produce the SCFA valerate [@Iino2007], and separate studies demonstrated valerate is depleted after clindamycin treatment and inhibited *C. difficile* growth *in vitro* and in C57BL/6 mice [@Jump2014; @McDonald2018]. Similarly, *Acetatifactor* can produce acetate and butyrate [@Pfeiffer2012], SCFAs that are decreased in mice with prolonged *C. difficile* infection after antibiotic treatment [@Lawley2012]. Thus protective bacteria and their metabolites could be depleted by osmotive laxative treatment depending on the timing and duration of treatment.

One possible explanation for the prolonged *C. difficile* colonization in 5-day PEG treated mice, might be due to the bacteria's persistence in the mucosal compartment. In fact, it has been hypothesized that *C. difficile* biofilms may serve as reservoirs for recurrent infections [@Frost2021] and *C. difficile* biofilms in the mucus layer were recently identified in patients as aggregates with *Fusobacterium nucleatum* [@Engevik2021]. There was an interesting pattern of increased *Enterobacteriaceae*, *Bacteroides*, and *C. difficile* in both the stool and mucosal communities of PEG-treated mice suggesting a potential synergy. *Bacteroides* has the potential to degrade mucus and the osmotic laxative may have allowed *Bacteroides* to colonize the mucosal niche by degrading mucin glycans with glycosyl hydrolases that are absent in *C. difficile* [@Engevik2020]. *Bacteroides* persistence in the mucosal tissue might also have helped *Enterobacteriaceae* to colonize the region, as a synergy between mucus-degrading *B. fragilis* and *E. coli* has previously been described [@Dejea2018]. A separate study demonstrated *C. difficile* was present in the outer mucus layer and associated with *Enterobacteriaceae* and *Bacteroidaceae* using fluorescent in situ hybridization (FISH) staining [@Semenyuk2015]. However, protective roles for *Bacteroides* have also been demonstrated. For example, *B. fragilis* prevented CDI morbidity in a mouse model and inhibited *C. difficile* adherence *in vitro* [@Deng2018]. In coculture experiments, *B. longum* decreased *C. difficile* biofilm formation while *B. thetaiotamicron* enhanced biofilm formation [@Normington2021] and *B. dorei* reduced *C. difficile* growth in a 9-species community *in vitro* [@Hassall2021]. Therefore, whether *Bacteroides* is detrimental or beneficial in the context of *C. difficile* infection or colonization is still unclear, but the niche and interactions with other bacteria may contribute.

*Akkermansia* is also a mucin degrader with potentially beneficial or detrimental roles depending on context in other diseases [@Cirstea2018; @BorgesCanha2015]. In our study, the relative abundance of *Akkermansia* shifted over time between groups of mice that either cleared *C. difficile* or had prolonged colonization. In the stool it was initially increased in mice that cleared *C. difficile*, but shifted after 5-days post-challenge so that it was increased in mice that had prolonged colonization. In the context of CDIs, some studies suggest a protective role [@Pereira2020; @Rodriguez2016], while others suggest a detrimental role because *Akkermansia* was positively correlated with *C. difficile* [@Sangster2016; @Vakili2020a; @Vakili2020b; @Li2019]. Because the relative abundance of *Akkermansia* was dynamic in our study, it is unclear whether *Akkermansia* helps with clearance of *C. difficile* or allows it to persist. A better understanding how *C. difficile* interacts with the mucosal microbiota may lead to insights into CDIs, asymptomatic *C. difficile* carriage, and colonizatiion resistance.
